Discordance LV - TF

### 2023-06-07 reporting/discordance LV TF.Rmd
update results

```{r eval=TRUE, fig.cap="Original plot", fig.height=20, include = TRUE, out.height=700, out.width=700, echo=FALSE}
knitr::include_graphics("images/comparison_methods6-1.png")
```

@@

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=20, include = TRUE, out.height=700, out.width=700, echo=FALSE}
knitr::include_graphics("images/plot_original.png")
```

>>>>

```{r eval=TRUE, fig.cap="Original plot", fig.height=6, echo=FALSE}
knitr::include_graphics("images/comparison_methods6-1.png")
```

@@

```{r eval=TRUE, fig.cap="New plot (fails to replicate)", fig.height=6, echo=FALSE}
knitr::include_graphics("images/plot_original.png")
```
